Modular analysis of gene expression data with R

### 2009-12-11 isanote/modular.tex
isanote: redesign the figure, update caption.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{isa2workflow3}
\caption{Work flow of a typical modular analysis study, with the
  \Rpackage{eisa} package (left); and four bicluster visualization
  techniques (right). The input of the \Rpackage{eisa} pipeline is a
  BioConductor \Rclass{ExpressionSet} object. This is normalized to
  $Z$-scores (1); the ISA iterations are initiated using ``smart'' or
  random seeds (2); and the biclusters are then merged and filtered
  based on the robustness measure (3). The \Rpackage{eisa} package
  contains tools to perform many GO, KEGG, etc. enrichment calculations
  quickly (4), and several bicluster visualization tools (5).
  Subfigures \subfig{A}, \subfig{B}, \subfig{C} and \subfig{D} were
generated
  using the acute lymphoblastic leukemia data set, see
  \citep{chiaretti04} and the \Rpackage{ALL} R package.
  \subfig{(A)} A condition plot for a simple bicluster. Each sample is
  represented as a bar, its height is its score in the bicluster.
  Samples above the red (none in this case) and samples
  below the green line are part of the biclusters. The coloring
  indicates cases and controls.
  \subfig{(B)} A module tree. Each rectangle is a bicluster; see the
  definition of the edges in the text. The modules are colored
  according to their Gene Ontology enrichment $p$-values, the codes of
  the enriched GO categories are shown in the top-left corner of the
  rectangles. The top-right corner shows the number of genes and
  conditions in the bicluster. The gene thresholds used for finding
  the modules is shown on the horizontal axes.
  \subfig{(C)} Heatmap for a single module, showing correlated
  expression for the genes and samples. The red lines are the gene and
  sample scores.
  \subfig{(D)} Profile plot, for a single module. On the top plot the
  expression of all samples is plotted, the samples of the module
  with black. The red and green lines show the mean of the two
  groups. The bottom plot is the same for the genes of the module.
}
\label{fig:workflow}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{isa2workflow3}
\caption{\subfig{(A)} Work flow of a typical modular analysis study, with the
  \Rpackage{eisa} package. The input of the \Rpackage{eisa} pipeline is a
  BioConductor \Rclass{ExpressionSet} object. This is normalized to
  $Z$-scores (1); the ISA iterations are performed (2); and the
  biclusters are then merged and filtered based on the robustness
  measure (3). The \Rpackage{eisa} package contains tools to perform
  many GO, KEGG, etc. enrichment calculations quickly (4), and several
  bicluster visualization tools (5).
  Subfigures \subfig{B} and \subfig{C} were generated
  using the acute lymphoblastic leukemia data set, see
  \citep{chiaretti04} and the \Rpackage{ALL} R package.
  \subfig{(B)} Heatmap for a single module, showing correlated
  expression for the genes and samples. The red lines are the gene and
  sample scores.
  \subfig{(C)} A module tree. Each rectangle is a bicluster; see the
  definition of the edges in the text. The modules are colored
  according to their Gene Ontology enrichment $p$-values, the codes of
  the enriched GO categories are shown in the top-left corner of the
  rectangles. The top-right corner shows the number of genes and
  conditions in the bicluster. The gene thresholds used for finding
  the modules is shown on the horizontal axes.
}
\label{fig:workflow}
\end{figure*}
